Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375

### 2015-02-12 papers/B1555_EdgeOn/B1555_letter.tex
new update to Discussion[complete]

Base on the fact that surface brightness is sensitive to perturbations in gravitational potential, flux ratio anomalies has been shown as one of the most effective methods to detect substructures \citep{Dalal2002} (more ref). Until now there are a dozen(?) known flux ratio anomalous systems and the number must increase in the future survey. Radio data provides reliable positions and fluxes of source for constraint and modeling because it avoids the problem of severe extinction and micro lensing from stars. On the other hand, optical or near infrared imaging also gives useful information about the lensing system. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modeling. The lack of knowledge about host galaxy, e.g. modeling with radio data alnog, may lead to an inapropreiate lens model.

Searching substructures with flux ratio anomalies 
we must be certain that perturbation are from substructure rather than other reason

In the SHARP IR imaging, we notice that edge-on disk
Previously studies assume that smooth potential from host galaxy is not possible to cause flux ratio anomaly.
We present new lens models of B1555+375 with a bulge and an edge-on disk. Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B. In our modeling, substructure is not neccessary to exist to cause the observed flux ratio anomaly. This indicates the flux ratio anomaly in B1555+375 is resulted from the structure of lens galaxy itself, which is the edge-on disk seen in the SHARP infrared imaging. Our result is consistent with the conclusion from  \citet{Xu14}. Their simulation gives a low probability on the hypothesis that substructure causing flux anomaly in B1555+375.

@@

Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems. The radio and narrow band observations are the best approaches to obtain accurate flux ratio data. However, optical and infrared imaging can provide more information on the structure of lens galaxy, which is also an important part in analyzing flux anomalous systems since we've shown that an edge-on disk can cause flux ratio anomaly. Our follow up will be explore more flux anomalous SHARP systems that we also notice a recognizable edge-on disk in the infrared imaging. As shown in Figure 3, the flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\

>>>>

Base on the fact that surface brightness is sensitive to perturbations in gravitational potential, flux ratio anomalies has been shown as one of the most effective methods to detect substructures \citep{Dalal2002} (more ref). Until now there are a dozen(?) known flux ratio anomalous systems and the number must increase in the future survey. Radio data provides reliable positions and fluxes of source for constraint and modeling because it avoids the problem of severe extinction and micro lensing from stars. On the other hand, optical or near infrared imaging also gives useful information about the lensing system. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modeling. The lack of knowledge about lens galaxy, e.g. modeling with radio data alnog, may lead to an improper lens model.

The idea of detecting substructures with flux ratio anomalies assumes that lens galaxy has completely smooth gravitational potential. Thus the perturbation is considered to be from faint satellite galaxy or ``dark'' subhalo. Numerical simulations have examined this approach with unkown systems. In \citet{Xu14}, only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos. The rest of them are only few percent likely or very unlikely to have their flux anomalies due to substructure, including B1555+375. Their results support that even using radio data, there are other possible reasons could cause flux anomalies. The answer to this concern may be explained by the high resolution IR imaging. In the SHARP K-band imaging of B1555+375, an edge-on disk lies across between the positions of radio merging double A \& B.

In sec. 2, we present new lens models of B1555+375 with a bulge and an edge-on disk. Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B. In our modeling, substructure is not neccessary to exist to cause the observed flux ratio anomaly. This indicates the flux ratio anomaly in B1555+375 is resulted from the structure of lens galaxy itself, which is the edge-on disk seen in the SHARP infrared imaging. Our result is consistent with the conclusion from \citet{Xu14}. Their simulation gives a low probability on the hypothesis that substructure causing flux anomaly in B1555+375.

@@

Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems. The radio and narrow band observations are the best approaches to obtain accurate flux ratio data. However, optical and infrared imaging can provide more information on the structure of lens galaxy. With the first system being analyzed and shown that an edge-on disk can cause flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
